SimResults_Bross

### 2024-08-01 bross/simResults_bross.Rmd
simResults_bross not sure why it is showing an error message:  all connections are in use

```{r change a to load upto 1000 datasets, warning=FALSE, cache=TRUE}}
# change to 1000 later
a <- 8

@@

>>>>

```{r initialization before for-loop, warning=FALSE, cache=TRUE}}
# 'a' ranges from 1 to 1000 to change the number of datasets loaded in each for loop
a <- 1000

@@

```{r check intermediate results for each data, warning=FALSE, cache=TRUE}
# check RD & SE by bross for each data, print:
#   sum.RD_bross.n, sum.RD_bross.ER.n, or sum.RD_bross.OR.n
#   where "n" is a number ranges from 1 to 1000
#   e.g.
sum.RD_bross.1
sum.RD_bross.ER.2

# check proxy selected by bross for each data, print:
#   proxy_bross.n, proxy_bross.ER.n, or proxy_bross.OR.n
#   where "n" is a number ranges from 1 to 1000
#   e.g.
proxy_bross.1
proxy_bross.ER.5
```
